---
title: "Avatar: The Last Airbender"
date: 2020-08-14
output: html_output
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

install.packages("tidytext")


library(tidyverse)
library(tidytuesdayR)
library(tidytext)
library(tvthemes)
library(ggrepel)

```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2020-08-11")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```




```{r }
#select data
avatar <- tt$avatar
colnames(avatar)
view(avatar)
head(avatar$character_words)

```


plotting imdb rating against chapter number

```{r }

chap.rating <- avatar %>% 
  group_by(book_num) %>% 
  distinct(chapter_num, imdb_rating) %>% 
  ggplot(aes(x = chapter_num, y = imdb_rating)) +
  geom_col() +
  facet_wrap(~ book_num)
```




lets see how many time the Aang's name is called in each chapter

```{r}
Aang <- avatar %>%
  select(book, book_num, chapter_num, character, character_words) %>%
  unnest_tokens(output = word, input = character_words) %>%
  filter(word %in% c("aang", "aang's")) %>%
  mutate(aa = 
           case_when(word == "aang" ~ 1,
                        word == "aang's" ~ 1))


#tell ggplot I need in this order 
Aang$book <- factor(Aang$book, levels=c("Water", "Earth", "Fire"))

#making the plot

Aang.plot <- Aang %>%
  group_by(book) %>%
  ggplot(aes(x = chapter_num, y = aa,
             label = character,
             fill = factor(character))) + 
  theme_avatar() +
  labs(title = "Number of times Aang's name is called in each episode", x =
         "Episode number", y = "Count", fill = "Character mentioning Aang's name") + 
  geom_col() +
  facet_wrap( ~ book)+
  theme(legend.title = element_text(size = 9), 
               legend.text = element_text(size = 9)) + 
  guides(shape = guide_legend(override.aes = list(size = 0.5))) +
  ggsave("Avatar_plot.png", width = 9, height = 7)
  
  
Aang.plot 


```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}


  
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "My TidyTuesday Plot.png",
  device = "png")

```
